---
title: "Final Project"
output: html_document
---

# Introduction 

The purpose of this project is to generate a model that will predict what makes for a good/bad Tinder experience.

# What is Tinder?

Tinder is an online dating and geosocial networking application in which users can "swipe right" or "swipe left" in order to like or dislike another user's profile. The application uses a "double opt-in" system where both users must match before they can exchange messages.

# Benefits of this model

Reviews of a mobile application can give us valuable insights about what works, what doesn't work, what should work, and what shouldn't work. In this case, Tinder can take these reviews to make the necessary changes in ensuring that current and future users will have the best experience as possible when active on the app.


# Loading Data and Packages
```{r}
library(tidymodels)
library(tidyverse)
library(readr)
library(ggplot2)
tinder_reviews <- read_csv("~/Downloads/tinder_google_play_reviews.csv")
View(tinder_reviews)
```


# Data Cleaning

While the dataset is relatively organized, we are going to clean the data even further to only contain the necessary variables and information needed for our data analysis.

```{r}
#creating and adding date column 
tinder_reviews$date = substr(tinder_reviews$at,1,10)
tinder_reviews$date = as.Date(tinder_reviews$date)

#selecting only necessary columns 
tinder <- tinder_reviews %>%
  select(content,score,date) 

#check for any missing values
is.na(tinder)
```

# Data Splitting

The data was split in a 80% training, 20% testing split. Stratified sampling was used to ensure that each subgroup (individuals rating the app from 0-5) receives proper representation within the sample.

```{r}
set.seed(2022)
tinder_split <- tinder %>%
  initial_split(prop = 0.8, strata = "score")

tinder_train <- training(tinder_split)
tinder_test <- testing(tinder_split)
```

The training data set has about 426,000+ observations, while the testing data set has almost 107,000 observations.

